SemanticPaint

### 2015-12-04 cv3d_seminar/paper.tex
meanfield inference

% \documentclass[journal, a4paper]{IEEEtran}
\documentclass{llncs}
\usepackage{llncsdoc}

\usepackage{graphicx}   
% \usepackage{url}
\usepackage{amsmath}

@@

\section{Dynamic Conditional Random Field}
Conditional Random Field (CRF) [Lafferty et al.2001].

 Conditional Random Fields are often used for segmentation \cite{related_work}, where availability of all data is assumed. Here, the underlying model changes constantly (new frames, labels or different SRF prediction), which requires a novel inference alogorithm. The class of each voxel is modeled by a random variable $x_i$. The label distribution over the volume $\mathcal{V}$ factorizes into likelihood terms $\psi_i(x_i)$ and prior terms $\psi_{ij}(x_i, x_j)$. Let $\mathcal{E}_i$ be a neighbourhood of $v_i$, $\mathbf{D}_t $ volumetric data at time $t$ and $\mathbf{x}$ a vector of all $x_i$. The posterior distribution is given by

@@

Unary and pairwise potentials $\phi_i(x_i)$ and $\phi_{ij}(x_i, x_j)$ encode the cost of assigning label to $v_i$ and a cost of assuming different labels by voxels in a neighbourhood, respectively. They are constatly changing due to the chainging predictions of the random forest and user interaction.

Initially, all voxels are encouraged to take a background label by setting $\phi_i(l) = 0$ for background class and grater than zero otherwise. Later, these are replaced by the random forest predictions for each voxel and as a result of user interactions.

When the user touches an object, a set of touched voxels $\mathcal(H)_S$ is registered. Their unary potentials are set to $\phi_i(l) = \infty$ if their labels are different then the specified one, and zero if the same, thus imposing the labeling. If user labels a region more than once, the old labeling are simply overwritten.

To process the encircling action, the labeling is projected into the current frame. Next, a GMM is fittend with the foreground class taken as a convex hull of the encirvled region and background as the rest of the image. For every pixel in a bounding box around the user annotation the unary potential are updated as

@@

Smoothness is achieved by the standard Potts model by assigning a disconuity cost $\phi_{ij}(x_i, x_j) = \lambda_{ij}$ if voxels have different labels and zero otherwise, with $\lambda_{ij}$ a function of difference in position, intensity and normal directions.

@@

\section{Putting it All Together}

@@

  \bibitem{TSDF}
  C URLESS , B. AND L EVOY , M. 1996. A volumetric method for building complex models from range images. In Proceedings of the 23rd annual conference on Computer graphics and interactive techniques. ACM, 303–312.

  \bibitem{hashed_voxel}
  N IESSNER , M., Z OLLH OFER , M., I ZADI , S., AND S TAMMINGER , M. 2013. Real-time 3D reconstruction at scale using voxel hashing. ACM TOG 32, 6

  \bibitem{online_forest}
  S AFFARI , A., L EISTNER , C., S ANTNER , J., G ODEC , M., AND B ISCHOF , H. 2009. On-line random forests. In IEEE ICCV Workshop.

  \bibitem{reservoir}
  [Vitter 1985]

  \bibitem{sift}
  L OWE , D. G. 1999. Object recognition from local scale-invariant features. In Proc. ICCV.

\end{thebibliography}

% Your document ends here!
\end{document}

>>>>

\documentclass{llncs}
\usepackage{llncsdoc}

\usepackage{graphicx}   
\usepackage{amsmath}

@@

  The GPU implementation can handle up to 17 million voxel classifications per second, while between 3 and 10 million voxels are visible at any one time \cite{hashed_voxel}. To improve performance, voxels are batched and only 1 batch is evaluated per frame.

\section{Dynamic Conditional Random Field}

 Conditional Random Fields are often used for segmentation \cite{related_work}, but they usually assume availability of all data. Here, a pairwise CRF \cite{crf} with a time dependent underlying model is used. It requires a novel inference alogorithm that can handle updates of the geometry and user specified labes. The class of each voxel is modeled by a random variable $x_i$. The label distribution over the volume $\mathcal{V}$ factorizes into likelihood terms $\psi_i(x_i)$ and prior terms $\psi_{ij}(x_i, x_j)$. Let $\mathcal{E}_i$ be a neighbourhood of $v_i$, $\mathbf{D}_t $ volumetric data at time $t$ and $\mathbf{x}$ a vector of all $x_i$. The posterior distribution is given by

@@

  Unary and pairwise potentials $\phi_i(x_i)$ and $\phi_{ij}(x_i, x_j)$ encode the cost of assigning a label to $v_i$ and a cost of assuming different labels by voxels in a neighbourhood, respectively. These costs are constatly changing due to the chainging predictions of the random forest and user interaction.

  Initially, all voxels are encouraged to take a background label by setting $\phi_i(l) = 0$ for background class and grater than zero otherwise. When the user touches an object, a set of touched voxels $\mathcal{H}_S$ is registered and their unary potentials set to $\phi_i(l) = \infty$ if their labels are different then the specified one, and zero if they are the same, thus imposing the labeling. If user labels a region more than once, the old labelings are simply overwritten.

  To process the encircling action, the labeling is projected into the current frame. Next, a GMM is fitted with the foreground class taken as a convex hull of the encirvled region and background as the rest of the image. For every pixel in a bounding box around the user annotation the unary potential are updated as

@@

  For all voxels that haven't been explicitly labaled by the user unitary potentials are updated with the random forest predictions as $\phi_i(l) = -\log P_F(x_i = l | \mathbf{D})$. Finally, smoothness is achieved by the standard Potts model by assigning a disconuity cost $\phi_{ij}(x_i, x_j) = \lambda_{ij}$ if voxels have different labels and zero otherwise, with $\lambda_{ij}$ a function of difference in position, intensity and normal directions.

@@

The mean-field inference algorithms follows \cite{inference}. It is adapted to the GPU programming model and to the constantly changing energy landscape. First, the original prbability distribution $P(\mathbf{x})$ is approximated by $Q(\mathbf{x})$ under KL-divergence $KL(Q||P)$.  It is chosen such that the marginal of each random variable is independent, that is $Q(\mathbf{x}) = \prod_i Q_i(\mathbf{x)_i})$. It is iteratively refined with updates derived from the fixed point of KL-divergence \cite{kl} as

\begin{equation}
 Q_i^t(l) = \frac{1}{Z_i}e^{M_i(l)} \text{, } t = 1, \ldots, T
\end{equation}
\begin{equation}
 M_i(l) = \phi_i(l) + \sum_{l' \in \mathcal{L}} \sum_{j \in \mathcal{N}(i)} Q_j^{t-1}(l')\phi_{ij}(l, l')
\end{equation}
\begin{equation}
 Z_i = \sum_{i \in \mathcal{L}} e^{-M_i(l)}
\end{equation}
\begin{equation}
 x_i^\star = \arg \max_{l \in \mathcal{L}} Q_i^T(l)
\end{equation}

It is guaranteed to converge under some conditions \cite{inference}. However, these guarantees do not hold here due to changing energy landscape. Moreover, the energy distribution is assumed to change only gradualy instead of initializing enerrgies at a given frame from a uniform distribution, it is initialized with the energies of the previous frame. It works well in practice, speeds up the process and allows visually pleasing label propagation effect.

SRF classification results would impact the final segmentation after several frames due to their effect on unitary potential. To speed up the process, however, the initial energy value at a new frame is taken as a weighted sum of the value from the previous frame and the SRF prediction, that is

\begin{equation}
 \widetilde{Q}_i^t(x_i) = \gamma Q_i^{t-1}(x_i) + (1 - \gamma) P_F^{t-1}(x_i = l | \mathbf{D}) \text{, } \gamma \in [0, 1]
\end{equation}

\section{Putting it All Together}
\section{Results}
\section{Future Work}
\section{Conclusions}

@@

  \bibitem{TSDF}
  CURLESS , B. AND LEVOY , M. 1996. A volumetric method for building complex models from range images. In Proceedings of the 23rd annual conference on Computer graphics and interactive techniques. ACM, 303–312.

  \bibitem{hashed_voxel}
  NIESSNER , M., Z OLLH OFER , M., IZADI , S., AND STAMMINGER , M. 2013. Real-time 3D reconstruction at scale using voxel hashing. ACM TOG 32, 6

  \bibitem{online_forest}
  SAFFARI , A., LEISTNER , C., SANTNER , J., G ODEC , M., AND BISCHOF , H. 2009. On-line random forests. In IEEE ICCV Workshop.

  \bibitem{reservoir}
  VITTER , J. S. 1985. Random sampling with a reservoir. ACM TOMS 11, 1.

  \bibitem{sift}
  LOWE , D. G. 1999. Object recognition from local scale-invariant features. In Proc. ICCV.

  \bibitem{crf}
  LAFFERTY , J., M C C ALLUM , A., AND PEREIRA , F. C. 2001. Conditional random fields: Probabilistic models for segmenting and labeling sequence data.

  \bibitem{inference}
  [Kr ̈ahenb ̈uhl and Koltun 2011]

  \bibitem{kl}
  [Koller and Friedman 2009]

\end{thebibliography}
\end{document}
